---
title: |
  | Building a Thesis in `Bookdown` and LaTeX, which can have a  
  | Wrapped Title if Long
# Your thesis title should be inverted pyramid-shaped, with the longest
# line on top and shorter lines below. Add a new line as tab-|-space-Words
author: 'Cosmo Cougar'
# This is the date of graduation
date: 'Month 20XX'
committeechair: Brigham Young
committeemembers: 
  - name: Karl G. Maeser
  - name: Harvey Fletcher
keywords: 'engineering, optimization, document creation'
# Class options are simple/fancy, masters/phd, and twoside (use twoside for printed thesis only)
layout: 'fancy, masters,twoside' 
# if you are using this for an honors thesis, you can leave off the degree in 
# layout and specify a degree below
degree: Master of Science
department: 'Department of Civil and Construction Engineering'

site: bookdown::bookdown_site

# Note that a tab is needed on the line after the `|`.
abstract: |
  This document describes the use of a new \LaTeX \ template for writing masters
  theses at Brigham Young University. This was made necessary by the relative age
  and complication of prior templates. Additionally, the new `cosmodown` R package
  contains an implementation of this thesis in R markdown, with the help of the 
  [`thesisdown`](https://github.com/ismayc/thesisdown) package.

  The abstract of a thesis should describe the
  motivation, objective, overall results, and central findings of the thesis.
  It may have multiple paragraphs if necessary.

  
acknowledgments: |
  Students should acknowledge funding sources. They may also use the
  acknowledgment page to express appreciation for the committee members, friends
  or family who provided assistance in research, writing or technical aspects of
  the dissertation, thesis or selected project. Acknowledgements should be simple
  and in good taste.

  
# Specify the location of the bibliography below
bibliography: [book.bib, packages.bib]
bibheadname: "References"
# Download your specific csl file from https://www.zotero.org/styles and refer to it in the line below.
csl: apa.csl
lot: true
lof: true
---

# About

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports; for example, a math equation $a^2 + b^2 = c^2$.

## Usage 

Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading.

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Render book


You can render the HTML version of this example book without changing anything:

1. Find the **Build** pane in the RStudio IDE, and

1. Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
